Strotor: A Minimalistic Approach to \\ Exploring Hierarchical Data

### 2014-08-24 paper/UIST2014/paper.tex
moved paper => paper/UIST2014

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
\caption{4-button controllers on a small mp3 player and AppleRemote.}
\label{u10}
\end{figure}

@@

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique and device called ``{\ST}'',
where users can explore large hierarchical database by simple rotating operations.

@@

{\ST}'s behavior is based on the following simple principles.
Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
They can be generated either by rotating the {\ST} device or typing a keyboard.

\begin{enumerate}
\item A portion of the hierarchical data is listed to the user.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People trying Strotor at an exhibition.}
\label{exhibition}
\end{figure}

>>>>

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
\caption{4-button controllers on a small mp3 player (left) and AppleRemote (right).}
\label{u10}
\end{figure}

@@

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using only 2 keys.
In that case, we can use a rotating device like a disk or a cylinder for the navigation,
since the device can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
%
% We have developed a new navigation technique where only two keys are required
% for exploring large hierarchical data, and implemented the system on
% a rotating device ``Strotor''.
%
We have developed a new navigation technique and device called ``{\ST}'',
where users can explore a large hierarchical database by simple rotating operations.

@@

Interaction with {\ST} is based on the following simple principles.
Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
They can be generated either by rotating the {\ST} device or typing a keyboard.

\begin{enumerate}
\item A portion of the hierarchical data is shown to the user.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right trying Strotor at an exhibition.}
\label{exhibition}
\end{figure}
